|

### 2020-08-06 paper.Rmd
Fig 1 formatting.

ggplot(proj_points, aes(x, y)) +
  geom_hex(bins = 20, aes(fill=log(..count..))) +
  scale_fill_viridis_c() +
  theme_bw() +
  facet_wrap(~p, scales = "free") +
  guides(fill = FALSE) +
  theme_void() + 
  theme(#axis.title.x=element_blank(), 
        #axis.title.y=element_blank(), 
        aspect.ratio = 1)

>>>>

ggplot(proj_points, aes(x, y)) +
  geom_hex(bins = 20, aes(fill=log(..count..))) +
  scale_fill_viridis_c() +
  facet_wrap(~p, scales = "free") +
  guides(fill = FALSE) +
  theme_bw() +
  theme(axis.title.x=element_blank(), 
        axis.title.y=element_blank(),
        axis.ticks.x = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text = element_blank(),
        aspect.ratio = 1)
